\LARGE \bf ***

### 2020-09-23 icra-2021.tex
minor fixes

Precision agriculture is rising in demand for reducing waste, costs, and resources while increasing outputs and utilization~\cite{hajjaj2014review}. Researchers have fulfilled some of these demands applying mobile robots in agricultural scenarios such as harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, where complex monitoring strategies, often implemented utilizing unmanned aerial vehicles (UAVs), are usually required for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}. Planning a mission for UAVs operating in such scenarios is a challenging task. It usually requires advanced levels of autonomy along with strictly limited energy budgets--with the typical instance being a UAV used to inform its grounded counterparts of obstacles detected while flying. Currently, UAVs in precision agriculture are semi-autonomous, in the sense that the path is static and defined using a mission planning software~\cite{daponte2019review}. The presented approach proposes an \emph{energy-aware dynamic mission planning algorithm} for UAVs for precision agriculture that overcomes the traditional planning and addresses the broader problem of increasing \emph{computational demands} and their relation to the UAV's energy consumption, path, and autonomy.

Although underrepresented in precision agriculture literature, energy planning algorithms for mobile robots are not a new concept and have been extensively studied, being these correlated to such topics as trajectory generation and path planning. Generally, they account for the energy due to the trajectory, by e.g., maximizing the operation time~\cite{wahab2015energy}, but practically restrict to a narrow class of mobile robots~\cite{kim2005energy}, and focus on optimizing motion control for such robots~\cite{kim2008minimum}. In a similar setting, rotorcrafts have been an obvious object of research interest, with algorithms such as energy-efficient trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}. Conversely, the algorithm presented here attempts to combine and generalize some of these technical breakthroughs and correlate the extensively studied energy planning to the growing computational demands of precision agriculture UAVs through a mission-aware perspective.
The technique of coupling the energy due to the computations performed and trajectory traveled inspires notably the algorithm, although such technique being, likewise the others, limited to the trajectory~\cite{mei2004energy,mei2005case,mei2006deployment}, or to the class of mobile robots~\cite{sadrpour2013mission,sadrpour2013experimental}.

@@

Starting with a position $\mathbf{p}\in\mathbb{R}^3$ in the 3D Euclidean space w.r.t. some inertial navigation frame $\mathcal{O}_W$, a guidance action--which allows the motion along the 3-axis--is built upon the direction to follow and derived using a vector field~\cite{de2017guidance}. Before the guidance action, we need to define the path: a set of generic continuous twice differentiable TEEs $\varphi_k:\mathbb{R}^3\rightarrow\mathbb{R}$ (the TEE is being satisfied $\varphi(\mathbf{p})\rightarrow 0$ for all the approaching points).

The energy evolution $\mathbf{q}\in\mathbb{R}^j$ is built using Fourier analysis (the meaning of $j$ is clarified to the reader in Subsection~\ref{sec:energy-model}) and decomposed in the energy due to the trajectory (depending on TEEs), and the computations (on QoS)--an approach adapted from authors' earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.

>>>>

Precision agriculture is rising in demand for reducing waste, costs, and resources while increasing outputs and utilization~\cite{hajjaj2014review}, with researchers fulfilling some of the demands applying mobile robots in agricultural scenarios such as harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}. In these scenarios, complex monitoring strategies, often implemented utilizing unmanned aerial vehicles (UAVs), are usually required for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}. Planning a mission for UAVs operating in such scenarios is a challenging task. It usually requires advanced levels of autonomy along with strictly limited energy budgets--with the typical instance being a UAV used to inform its grounded counterparts of obstacles detected while flying. Currently, UAVs in precision agriculture are semi-autonomous, in the sense that the path is static and defined using a mission planning software~\cite{daponte2019review}. The presented approach proposes an \emph{energy-aware dynamic mission planning algorithm} for UAVs for precision agriculture that overcomes the traditional planning and addresses the broader problem of increasing \emph{computational demands} and their relation to the UAV's energy consumption, path, and autonomy.

Although underrepresented in precision agriculture literature, energy planning algorithms for mobile robots are not a new concept and have been extensively studied, being these correlated to such topics as trajectory generation and path planning. Generally, they account for the energy due to the trajectory, by e.g., maximizing the operational time~\cite{wahab2015energy}, but practically restrict to a narrow class of mobile robots~\cite{kim2005energy}, and focus on optimizing motion control for such robots~\cite{kim2008minimum}. In a similar setting, rotorcrafts have been an obvious object of research interest, with algorithms such as energy-efficient trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}. Conversely, the algorithm presented here attempts to combine and generalize some of these technical breakthroughs and correlate the extensively studied energy planning to the growing computational demands of precision agriculture UAVs through a mission-aware perspective.
The technique of coupling the energy due to the computations performed and trajectory traveled inspires notably the algorithm, although such technique being, likewise the others, limited to the trajectory~\cite{mei2004energy,mei2005case,mei2006deployment}, or to the class of mobile robots~\cite{sadrpour2013mission,sadrpour2013experimental}.

@@

Starting with a position $\mathbf{p}\in\mathbb{R}^3$ in the 3D Euclidean space w.r.t. some inertial navigation frame $\mathcal{O}_W$, we build a guidance action--which allows the motion along the 3-axis--to the path to follow using a vector field~\cite{de2017guidance}. The path is a set of generic continuous twice differentiable TEEs $\varphi_k:\mathbb{R}^3\rightarrow\mathbb{R}$ (the TEE is being satisfied $\varphi(\mathbf{p})\rightarrow 0$ for all the approaching points).

We build the energy evolution $\mathbf{q}\in\mathbb{R}^j$ using Fourier analysis (the meaning of $j$ is clarified to the reader in Subsection~\ref{sec:energy-model}) and decompose such evolution in the energy due to the trajectory (depending on TEEs), and the computations (on QoS)--an approach adapted from our earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.
